Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-07-05 introduction.tex
Fix latex and broken reference

In spite of the impressive scale of the ATLAS distributed computing system,
demand for computing systems will soon significantly outstrip current and
projected supply.   The data volumes that will need analyzing in LHC-Run 3 
($~\approx$ 2022) and the high-luminosity era (Run 4) will increase by factors
of 10-100 compared to the current phase (Run 2). There are multiple levels at
which this problem needs to be addressed: the utilization of emerging parallel
architectures (e.g., platforms); algorithmic and advances in analytical
methods (e.g., use of Machine Learning); and the ability to exploit different
platforms (e.g., clouds and supercomputers).

% As the LHC prepares for Run 3 in $~\approx$ 2022 and the high-luminosity era
% (Run 4), it is anticipated that the data volumes that will need analyzing
% will increase by factors of 10-100 compared to the current phase (Run 2).
% Data will be larger in volume but will also require more sophisticated
% computational processing.

@@

We demonstrate how Titan is more efficiently utilized by the mixing of small
and short-lived tasks in backfill with regular payloads. Cycles otherwise
unusable (or very difficult to use) are used for science thus, increasing the
overall utilization on Titan without loss of quality-of-service. The
conventional mix of jobs at OLCF cannot be effectively backfilled because of
size, duration, and scheduling policies. Our approach is extensible to any HPC
with "capability scheduling" policies.  We also investigate the use of a
pilot-abstraction based task execution runtime system to flexibly execute
ATLAS and other heterogeneous workloads (molecular dynamics) using regular
queues. As such, our approach provides a general solution and investigation of
the convergence of HPC and HTC execution of workloads.

@@

This paper also provides: (i) a critical evaluation of the many design and
operational considerations that have been taken to support the sustained,
scalable and production usage of Titan for historically high-throughput
workloads, and (ii) early lessons and guidance as the community looks forward
to designing the next generation of online analytical platforms~\cite{foap-
url}, for how current and future experimental and observational systems can be
integrated with production supercomputers in a general and extensible manner.

>>>>

In spite of the impressive scale of the ATLAS distributed computing system,
demand for computing systems will soon significantly outstrip current and
projected supply.   The data volumes that will need analyzing in LHC-Run 3
($~\approx$ 2022) and the high-luminosity era (Run 4) will increase by
factors of 10--100 compared to the current phase (Run 2). There are multiple
levels at which this problem needs to be addressed: the utilization of
emerging parallel architectures (e.g., platforms); algorithmic and advances
in analytical methods (e.g., use of Machine Learning); and the ability to
exploit different platforms (e.g., clouds and supercomputers).

% As the LHC prepares for Run 3 in $~\approx$ 2022 and the high-luminosity
% era (Run 4), it is anticipated that the data volumes that will need
% analyzing will increase by factors of 10-100 compared to the current phase
% (Run 2). Data will be larger in volume but will also require more
% sophisticated computational processing.

@@

We demonstrate how Titan is more efficiently utilized by the mixing of small
and short-lived tasks in backfill with regular payloads. Cycles otherwise
unusable (or very difficult to use) are used for science thus, increasing the
overall utilization on Titan without loss of quality-of-service. The
conventional mix of jobs at OLCF cannot be effectively backfilled because of
size, duration, and scheduling policies. Our approach is extensible to any
HPC with ``capability scheduling'' policies.  We also investigate the use of
a pilot-abstraction based task execution runtime system to flexibly execute
ATLAS and other heterogeneous workloads (molecular dynamics) using regular
queues. As such, our approach provides a general solution and investigation
of the convergence of HPC and HTC execution of workloads.

@@

This paper also provides: (i) a critical evaluation of the many design and
operational considerations that have been taken to support the sustained,
scalable and production usage of Titan for historically high-throughput
workloads, and (ii) early lessons and guidance as the community looks forward
to designing the next generation of online analytical
platforms~\cite{foap-url}, for how current and future experimental and
observational systems can be integrated with production supercomputers in a
general and extensible manner.
